Flowers text analysis

### 2023-01-16 code/annotation_analysis.Rmd
work on paper and redo model summaries

show_summary_rstan <- function(model){
  badlist <- c("accept_stat__","divergent__","energy__","n_leapfrog__","sigma", "stepsize__","treedepth__")
  intervals <- gather_draws(model, `[a-zA-z_(): ]+`, regex=TRUE) |> mean_qi() |> filter(!.variable %in% badlist) |> 
    mutate(lower=round(.lower, digits=2),
           upper=round(.upper, digits=2),
           `Credible Interval`=str_c("[",lower,", ", upper,"]"),
           Term=.variable,
           Estimate=round(.value, digits=2)) %>% 
    select(Term, Estimate, `Credible Interval`)

@@

m1 <- stan_lmer(numword ~ trialNum + condition + (1|gameId)+ (1|player)+(1|flower), data=annotated) |> write_rds(here(model_path,"m1.rds"))
show_summary_rstan(m1) |> write_rds(here(model_path,"word_model.rds"))
```

```{r, eval=F, include=F}
m1 <- read_rds(here(model_path,"m1.rds"))
m1

@@

@@

m_samegame_sameflower <-  stan_lmer(sim ~ condition*earlier*same_player + 
                                      (1|game1)+(1|flower), data=within_game_flower) |> write_rds(here(model_path,"m2.rds"))

show_summary_rstan(m_samegame_sameflower) |> write_rds(here(model_path,"samegame_sameflower_model.rds"))

@@

m_samegame_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=within_game_between_flower) |> write_rds(here(model_path,"m3.rds"))

show_summary_rstan(m_samegame_diffflower) |> write_rds(here(model_path,"samegame_diffflower_model.rds"))

@@

```{r}
between_game_within_flower <- flower_all |> 
  filter(game1!=game2) |> 
  filter(ref1==ref2) |> 
  filter(later-earlier<3) |> 
  mutate(flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, flower)

m_diffgame_sameflower <-  stan_glm(sim ~ condition*earlier, data=between_game_within_flower) |> write_rds(here(model_path,"m4.rds"))

show_summary_rstan(m_diffgame_sameflower) |> write_rds(here(model_path,"diffgame_sameflower_model.rds"))

@@

m_to_end_sameflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_same_flower) |> write_rds(here(model_path,"m5.rds"))

show_summary_rstan(m_to_end_sameflower) |> write_rds(here(model_path,"to_end_sameflower_model.rds"))

@@

m_to_end_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_diff_flower) |> write_rds(here(model_path,"m5.rds"))

show_summary_rstan(m_to_end_diffflower) |> write_rds(here(model_path,"to_end_diffflower_model.rds"))

@@

m_within_end <-  stan_glm(sim ~ condition*same_flower*same_game, data=within_end) |> write_rds(here(model_path,"m6.rds"))

show_summary_rstan(m_within_end) |> write_rds(here(model_path,"within_end.rds"))

>>>>

show_summary_rstan <- function(model){
  badlist <- c("accept_stat__","divergent__","energy__","n_leapfrog__","sigma", "stepsize__","treedepth__")
  intervals <- gather_draws(model, `[a-zA-z_(): ]+`, regex=TRUE) |> mean_qi() |> filter(!.variable %in% badlist) |> 
    mutate(lower=round(.lower, digits=3),
           upper=round(.upper, digits=3),
           `Credible Interval`=str_c("[",lower,", ", upper,"]"),
           Term=.variable,
           Estimate=round(.value, digits=3)) %>% 
    select(Term, Estimate, `Credible Interval`)

@@

m1 <- stan_lmer(numword ~ trialNum + condition + (1|gameId)+ (1|flower)+(1|player), data=annotated) |> write_rds(here(model_path,"m1.rds"))

@@

```{r, eval=F}
 read_rds(here(model_path,"m1.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"word_model.rds"))
```

```{r}
foo <- read_rds(here(model_path,"m1.rds"))
gather_draws(foo, `[a-zA-z_(): ]+`, regex=TRUE) |> select(.variable) |> unique()
```

@@

m_samegame_sameflower <-  stan_lmer(sim ~ condition*earlier*same_player + 
                                      (1|game1)+(1|flower), data=within_game_flower) |> write_rds(here(model_path,"m2.rds"))
```

```{r, eval=F}
read_rds(here(model_path,"m2.rds")) |> 
show_summary_rstan() |> write_rds(here(model_path,"samegame_sameflower_model.rds"))

@@

m_samegame_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=within_game_between_flower) |> write_rds(here(model_path,"m3.rds"))
```

```{r, eval=F}
read_rds(here(model_path,"m3.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"samegame_diffflower_model.rds"))

@@

```{r, eval=F}
between_game_within_flower <- flower_all |> 
  filter(game1!=game2) |> 
  filter(ref1==ref2) |> 
  filter(later-earlier<3) |> 
  mutate(flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, flower)

m_diffgame_sameflower <-  stan_glm(sim ~ condition*earlier, data=between_game_within_flower) |> write_rds(here(model_path,"m4.rds"))
```

```{r, eval=F}
read_rds(here(model_path,"m4.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"diffgame_sameflower_model.rds"))

@@

m_to_end_sameflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_same_flower) |> write_rds(here(model_path,"m5.rds"))
```

```{r, eval=F}
read_rds(here(model_path,"m5.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"to_end_sameflower_model.rds"))

@@

m_to_end_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_diff_flower) |> write_rds(here(model_path,"m6.rds"))
```

```{r, eval=F}
read_rds(here(model_path,"m6.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"to_end_diffflower_model.rds"))

@@

m_within_end <-  stan_glm(sim ~ condition*same_flower*same_game, data=within_end) |> write_rds(here(model_path,"m7.rds"))

```{r, eval=F}

read_rds(here(model_path,"m7.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"within_end.rds"))
